\LARGE \bf Steering a Swarm Using Global Inputs and Swarm Statistics

### 2016-08-15 journalSwarmControl/expResults.tex
mary's edits on minimum
mean \pm std for numbers
added new swarm control code
updated mathematica images and removed 2 figs

\paragraph{Varying number}
\begin{figure}
\begin{overpic}[width = 0.5\columnwidth]{ResVaryNum.pdf}\end{overpic}
\begin{overpic}[width = 0.48\columnwidth]{measureLearning.pdf}\end{overpic}
\caption{
\label{fig:ResVaryNu}Data from \emph{Varying Number} using robots to push an object through a maze to a goal location.  (Left) Data indicates this task has an optimal number of robots, perhaps due to the relative sizes of the robots, obstacles, and object. Best-fit linear and quadratic lines are overlaid for comparison. 
(Right) Skill improves as players retry tests using data from \emph{Varying Number}.
}
\end{figure}

Transport of goods and materials between points is at the heart of all engineering and construction in real-world systems. This experiment varied from 1 to 500 the population of robots used to transport an object. The total area, maximum robot speed, and total net force the swarm could produce were constant. The robots pushed a large hexagonal object through an  {\sffamily S}-shaped maze. We hypothesized participants would complete the task faster with more robots. The results, shown in Fig.~\ref{fig:ResVaryNu}, do not support our hypothesis, indicating a minima around 130 robots.

>>>>

\paragraph{Varying number}
\begin{figure}
\begin{overpic}[width = 0.5\columnwidth]{ResVaryNum.pdf}\end{overpic}
%\begin{overpic}[width = 0.48\columnwidth]{measureLearning.pdf}\end{overpic}
\caption{
\label{fig:ResVaryNu}Data from \emph{Varying Number} using robots to push an object through a maze to a goal location.  Data indicates this task has an optimal number of robots, perhaps due to the relative sizes of the robots, obstacles, and object. Best-fit linear and quadratic lines are overlaid for comparison. 
%(Right) Skill improves as players retry tests using data from \emph{Varying Number}.
}
\end{figure}

Transport of goods and materials between points is at the heart of all engineering and construction in real-world systems. This experiment varied from 1 to 500 the population of robots used to transport an object. The total area, maximum robot speed, and total net force the swarm could produce were constant. The robots pushed a large hexagonal object through an  {\sffamily S}-shaped maze. We hypothesized participants would complete the task faster with more robots. The results, shown in Fig.~\ref{fig:ResVaryNu}, do not support our hypothesis, indicating a minimum around 130 robots.
